Disconnected pseudo-$C_\ell$ covariances for projected datasets

### 2019-05-21 draft/paper.tex
bs

%\usepackage{widetext}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb,amsmath,bm,dsfont}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{lipsum}
\newcommand{\nv}{\hat{\bf n}}
\newcommand{\kalo}{Karhunen-Lo\`{e}ve~}
\newcommand{\cfh}{CFHTLenS~}
\newcommand{\jcap}{JCAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apjs}{ApJS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\prd}{Phys.~Rev.~D}
\newcommand{\prl}{Phys.~Rev.~Lett.}
\newcommand{\aj}{Astron. Journal}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\procspie}{Proceedings of the SPIE}
\newcommand{\physrep}{Physics Reports}

@@

  \subsection{Preliminaries}
    We will deal with spin-0 and spin-2 fields defined on a 2-dimensional space. We will use a generic notation that can then be applied to both curved and flat skies. Given a field ${\bf a}({\bf x})$, with 1 (spin-0) or 2 components (spin-2), and defined on the coordinates ${\bf x}$, we define its generalized Fourier coefficients as
    \begin{equation}
      {\bf a}_{\bf k}=\summ{x}\,\Ylm{\dag}{k}{x}\,{\bf a}({\bf x}),
    \end{equation}
    where the operator $\summ{x}$ denotes a integral or sum of all coordinates ${\bf x}$, and $\Ylm{\dag}{k}{x}$ are a set of orthogonal functions. We will also assume that the $\Ylm{\dag}{k}{x}$ are a \emph{complete} set of basis functions, in which case:
    \begin{align}
      &\summ{x}\,\Ylm{\dag}{k}{x}\Ylm{}{l}{x}=\mathds{1}\Delta^x({\bf k},{\bf l}),\\
      &\summ{k}\,\Ylm{}{k}{x}\Ylm{\dag}{k}{y}=\mathds{1}\Delta^k({\bf x},{\bf y}),
    \end{align}
    where $\summ{k}$ denotes an integral over all possible generalised Fourier coefficients ${\bf k}$, and $\Delta^x$ and $\Delta^k$ are generalized delta functions:
    \begin{align}
      &\summ{k}\,f({\bf k})\Delta^x({\bf k},{\bf l})\equiv f({\bf l}),\\
      &\summ{x}\,f({\bf x})\Delta^k({\bf x},{\bf y})\equiv f({\bf y}).
    \end{align}

@@

    All the functions and operators above can be specialised to fields defined on the sphere or the 2D plane (flat sky) as follows:

@@

\subsection{$\chi^2$ distribution and covariance matrices}
Apart from checking that we recover the same cosmological predictions from the
covariance matrices from both the analytical approximation and the
simulations, we studied the differences between them.

@@

\section{Flat sky}

>>>>

%\usepackage{widetext}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb,amsmath,bm,dsfont}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{lipsum}
\newcommand{\nv}{\hat{\mathbf{\theta}}}
\newcommand{\kalo}{Karhunen-Lo\`{e}ve~}
\newcommand{\cfh}{CFHTLenS~}
\newcommand{\jcap}{JCAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apjs}{ApJS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\prd}{Phys.~Rev.~D}
\newcommand{\prl}{Phys.~Rev.~Lett.}
\newcommand{\aj}{Astron. Journal}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\procspie}{Proceedings of the SPIE}
\newcommand{\physrep}{Physics Reports}

@@

  \subsection{Preliminaries}
    We will deal with spin-0 and spin-2 fields defined on a 2-dimensional space. We will use a generic notation that can then be applied to both curved and flat skies. Given a field ${\bf a}({\bf x})$, with 1 (spin-0) or 2 components (spin-2), and defined on the coordinates ${\bf x}$, we define its generalized Fourier coefficients as
    \begin{equation}
      {\bf a}_{\bf k}=\summ{x}\,\Ylm{\dag}{k}{x}\,{\bf a}({\bf x}),
    \end{equation}
    where the operator $\summ{x}$ denotes a integral or sum of all coordinates ${\bf x}$, and $\Ylm{\dag}{k}{x}$ are a set of orthogonal functions. We will also assume that the $\Ylm{\dag}{k}{x}$ are a \emph{complete} set of basis functions, in which case:
    \begin{align}
      &\summ{x}\,\Ylm{\dag}{k}{x}\Ylm{}{l}{x}=\mathds{1}\Delta^x({\bf k},{\bf l}),\\
      &\summ{k}\,\Ylm{}{k}{x}\Ylm{\dag}{k}{y}=\mathds{1}\Delta^k({\bf x},{\bf y}),
    \end{align}
    where $\summ{k}$ denotes an integral over all possible generalised Fourier coefficients ${\bf k}$, and $\Delta^x$ and $\Delta^k$ are generalized delta functions:
    \begin{align}
      &\summ{k}\,f({\bf k})\Delta^x({\bf k},{\bf l})\equiv f({\bf l}),\\
      &\summ{x}\,f({\bf x})\Delta^k({\bf x},{\bf y})\equiv f({\bf y}).
    \end{align}
    For a spin-$s$ quantity, $\Ylm{}{l}{x}$ can be written in terms of a differential operator $\eth$ and a set of scalar orthogonal functions $q({\bf l},{\bf x})$ as:
    \begin{equation}
      \Ylm{}{l}{x}=-\frac{\beta_{\ell,s}}{2}\left(
      \begin{array}{cc}
        \eth^s+\bar{\eth}^s & i(\eth^s-\bar{\eth}^s)\\
        -i(\eth^s-\bar{\eth}^s) & \eth^s+\bar{\eth}^s
      \end{array}\right) q({\bf l},{\bf x}).
    \end{equation}

@@

    \begin{table*}
     \centering
     \begin{tabular}{|c|c|c|}
     \hline
      Mathematical object & Curved sky & Flat sky (continuum $\rightarrow$ discretized) \\
      \hline
      \(\displaystyle {\bf l} \) & \(\displaystyle (\ell,m) \) & \(\displaystyle (l_x,l_y) \) \\
      \(\displaystyle \summ{l} \) & \(\displaystyle \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell} \) & \(\displaystyle \int \frac{dl^2}{2\pi} \rightarrow \sum_{\bf k}\frac{2\pi}{L_xL_y}\) \\
      \(\displaystyle \Delta^x({\bf l},{\bf l}')\) & \(\displaystyle \delta^K_{\ell\ell'}\delta^K_{mm'}\) & \(\displaystyle 2\pi\,\delta^D({\bf l}-{\bf l}')\rightarrow \delta^K_{l_xl'_x}\delta^K_{l_yl'_y}\frac{L_xL_y}{(2\pi)^2}2\pi\) \\
      \(\displaystyle {\bf x}\) & \(\displaystyle \nv\equiv(\theta,\varphi) \) & \(\displaystyle (x,y)\) \\
      \(\displaystyle \summ{x} \) & \(\displaystyle \int_0^{\phi} d\phi \int_{-1}^{1} d(\cos\theta)\) & \(\displaystyle \int \frac{dx^2}{2\pi}\rightarrow\sum_{\bf x}\frac{L_xL_y}{2\pi N_xN_y}\) \\
      \(\displaystyle \Delta^k(\nv,\nv')\) & \(\displaystyle \delta^D(\cos\theta-\cos\theta')\delta^D(\varphi-\varphi')\) & \(\displaystyle 2\pi\,\delta^D({\bf x}-{\bf y})\rightarrow\delta^K_{xx'}\delta^K_{yy'}\frac{N_xN_y}{L_xL_y}2\pi\) \\
      \(\displaystyle q({\bf l},{\bf x})\) & \(\displaystyle Y_{\ell m}(\nv)\) & \(\displaystyle e^{i{\bf l}\cdot{\bf x}}\) \\
      \(\displaystyle \eth\,_sf\) & \(\displaystyle -(\sin\theta)^s\left(\partial_\theta+i\frac{\partial_\varphi}{\sin\theta}\right)(\sin\theta)^{-s}\,_sf(\nv)\) & \(\displaystyle (\partial_x-i\partial_y)\,_sf\) \\
      \(\displaystyle \bar{\eth}\,_sf\) & \(\displaystyle -(\sin\theta)^{-s}\left(\partial_\theta-i\frac{\partial_\varphi}{\sin\theta}\right)(\sin\theta)^s\,_sf(\nv)\) & \(\displaystyle (\partial_x+i\partial_y)\,_sf\) \\
      \(\displaystyle F \) & \(\displaystyle 1 \) & \(\displaystyle (2\pi)^{-1}\) \\
      \hline
     \end{tabular}
     \caption{Lookup table describing the generalized notation used here in for quantities defined on the sphere (second column) and on the flat 2D plane (third column). For the flat-sky case, we also provide expressions for a discretized, finite 2D plane with }

    \end{table*}

    All the functions and operators above can be specialised to fields defined on the sphere or the 2D plane (flat sky) as follows:
    Curved sky:

@@

\subsection{Visual inspection}
\todo{Rows plot para todas las combinaciones}
\todo{diff-correlation TTTT BBBB}
\todo{Eigenvalue plot}

\subsection{Quantitative checks}
\todo{Plot $\chi^2$ TT-TT, TE-TE, EE-EE}

\subsection{Contaminant deprojection}
\todo{}

\subsection{Impact on parameter estimation}
\todo{$\chi^2$ plot para 2 bines}
\todo{diff-correlaton plot para 2 bines ver Fig. 8  de 1809.09603}
\todo{Contours}

\subsection{$\chi^2$ distribution and covariance matrices - old section}
Apart from checking that we recover the same cosmological predictions from the
covariance matrices from both the analytical approximation and the
simulations, we studied the differences between them.

@@

\section{Flat sky}
\todo{Plot mascara}
\todo{Plot chi2 TT-TT TE-TE, EE-EE}
